### 2013-10-03 LaTeX/Abstract.tex
min edit

Our theoretical model states that the economic impacts of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.

>>>>

Our theoretical model states that the economic impact of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.
